Results

### 2025-04-08 notebooks/00_index.qmd
feat: mva of velocity

```{julia}
# along time get the temperature from anisotropic temperature
function tTemp(x; dims=Ti)
    return mean.(eachslice(x; dims))
end
```

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"
WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
```

@@

psp_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
    ];
    ylabel=n_ylabel
)

@@

tvars_psp = [
    tnorm_combine ∘ psp_B,
    psp_n,
    SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels),
    psp_temp,
]

mva_B = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
mva_V_labels = ["V_L", "V_M", "V_N"]
```

@@

event = psp_events[2, :]
# psp_ds(event["tstart"], event["tstop"])
plot_candidate(event, [tvars_psp; mva_B])
```

>>>>

```{julia}
# along time get the temperature from anisotropic temperature
function tTemp(x; dims=Ti)
    return mean.(eachslice(x; dims))
end

_unitify(u) = x -> x * u
mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
```

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"
WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"

mva_V_labels = ["V_L", "V_M", "V_N"]
```

@@

psp_n = SPEDAS.DataSet(
    "Density",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
        _unitify(u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels=["SPC Proton"]),
        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
    ];
    ylabel=n_ylabel
)

@@

psp_V = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels)

tvars_psp = [
    tnorm_combine ∘ psp_B,
    psp_n,
    psp_V,
    psp_temp
]
```

@@

psp_B_mva = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
psp_V_mva = Product("mva_V", (psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)

event = psp_events[2, :]
plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva]])
```
